Dynein walks like an Imperial AT-ST

### 2018-04-06 papers/paper/paper.tex
Add leading/lagging histogram to paper.pdf
Minor add to paper.

@@

\begin{figure*}[tbhp]
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_vs_step_length}
    \subcaption{Static unbinding rate}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_vs_step_length}
    \subcaption{Exponential unbinding rate}
  \end{subfigure}
\caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
\label{fig:lengthhist}
\end{figure*}

>>>>

\section*{Model}
\subsection*{Model layout}
The dynein model used in this paper consists of two systems meant to mimic the motor's dynamics in its post-powerstroke and pre-powerstroke states. These systems, shown in Figure \ref{fig:model-cartoon},

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.49\linewidth]{figures/onebound-cartoon.pdf}
\includegraphics[width=0.49\linewidth]{figures/bothbound-cartoon.pdf}
\caption{Cartoon representation of model systems. \textbf{Left}: Post-powerstroke, \textbf{right}: pre-powerstroke.}
\label{fig:duration-length}
\end{figure}

@@

\begin{figure*}[tbhp]
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_histogram}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_histogram}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_vs_step_length}
    \subcaption{Static unbinding rate}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_vs_step_length}
    \subcaption{Exponential unbinding rate}
  \end{subfigure}
\caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
\label{fig:lengthhist}
\end{figure*}
